### 2020-10-22 Thesis-Chapter3-Arguments.tex
Develop classical method section

\subsection{Characteristics}

@@

Rozenshtein reflects on the diagnosis positively:

@@

Embracing reality is the first step to dealing with it \cite{baker_2019}. In the next two sections, we look at
strategies for dealing with \acp{wicked-prob}.

@@

@@

@@

>>>>

\subsection{Characteristics}
\label{wicked-characteristics}

@@

Rozenshtein reflects on the diagnosis optimistically:

@@

Embracing reality is the first step to dealing with it \cite{baker_2019}. We have by now embraced the reality of
\acp{wicked-prob}. In the next two sections, we look at strategies for dealing with it.

@@

This section describes the two common current policymaking approaches, the classical analytical method and ``muddling
through.''

@@

The classical analytical method \cite{feeley_judicial_2000} (or ``the modern-classical model of planning''
\cite{rittel_dilemmas_1973}, ``traditional policy analysis'' \cite{rozenshtein_wicked_2018}, or ``linear thinking''
\cite{commission_tackling_2018}) has already been introduced. It is the reason-based method that functions by setting
goals, identifying problems, evaluating alternatives, implementing solutions, and analyzing outcomes in order to correct
errors. \myfig{fig-classical-method} illustrates the approach in the context of encryption and \ac{EA}. Per its name, it
has a linear flow from problem to solution. The refinement step reflects the fact that this method tracks outcomes and
tweaks solutions over time; however, refinement is always in-kind---it represents a reinforcement, as opposed to a
reassessment, of the chosen solution.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/OODA-classical.png}
  \caption[The Classical Analytical Method]{The Classical Analytical Method}
  \label{fig-classical-method}
\end{figure}

The shortcomings of the classical analytical method were discussed in \mysec{wicked-characteristics}. It fails due to
disagreement over goals, the dependence of the problem definition on the alternatives generated (violating the linear
flow), the inability to evaluate alternatives, and the lack of a definitive stopping rule.

@@

``Muddling through'' represents an alternative policy making strategy.

See \myfig{fig-muddling-through}.

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=0.55\linewidth]{dfds/build/OODA-muddling.png}
  \caption[The ``Muddling Through'' Method]{The ``Muddling Through'' Method}
  \label{fig-muddling-through}
\end{figure}
